---
title: "Youth_analysis_R_code"
format: html
editor: visual
---

# Packages loading

```{r}
#some may not be used in current analysis
library(semTools)
library(haven)
library(tidyverse)
library(dplyr)
library(bruceR)
library(summarytools)
library(gtsummary)
library(labelled)
library(lm.beta)
library(corrplot)
library(lavaan)
library(Gmisc)
library(psych)
library(parameters)
library(GPArotation)
library(finalfit)
library(demoGraphic)
library(vtable)
library(gtsummary)
library(janitor)
library(naniar)

library(rstatix)

library(ltm)

library(devtools)
library(lavaan)
library(semPlot)
library(OpenMx)
library(knitr)
library(kableExtra)
library(GGally)
library(simsem)
library(remotes)
library(tidySEM)
library(ggplot2)
library(labelled)

library(ggplot2)
library(cowplot)
library(jtools)
library(marginaleffects)
library(tidyquant)
library(ggdist)
library(ggsci)
```

# Data importation

```{r}
imported <- read_dta('youth_data.dta')
```

# Information of socio-demographic feature

## Create table of socio-demographic feature

```{r}
DEMO_dd <- imported %>% 
  mutate(age_cat = case_when(Q2_1 <= 19 ~ 1,
                             Q2_1 >= 20 & Q2_1 <= 24 ~ 2,
                             Q2_1 >= 25 & Q2_1 <= 29 ~ 3,
                             Q2_1 >= 30 & Q2_1 <= 34 ~ 4,
                             Q2_1 >= 35 & Q2_1 <= 40 ~ 5),
         new_Q2_2 = case_when(Q2_2 == 1 ~ 0, Q2_2 == 2 ~ 1),
         new_Q2_3 = case_when(Q2_3 == 1 | Q2_3 == 3 | Q2_3 == 4 ~ 1,
                              Q2_3 == 2 | Q2_3 == 5 | Q2_3 == 6 ~ 2),
         new_Q4 = case_when(Q4 <=5 ~ 0, Q4 >= 6 & Q4 <= 12 ~ 1),
         income_cat = case_when(Q2_7_inco == 1 | Q2_7_inco == 2 ~ 1,
                                Q2_7_inco == 3 | Q2_7_inco == 4 ~ 2,
                                Q2_7_inco == 11 | Q2_7_inco == 12 ~ 9,
                                Q2_7_inco == 5 ~ 3, Q2_7_inco == 6 ~ 4,
                                Q2_7_inco == 7 ~ 5, Q2_7_inco == 8 ~ 6,
                                Q2_7_inco == 9 ~ 7, Q2_7_inco == 10 ~ 8)) %>% 
  mutate(across(c(new_Q2_2,age_cat,new_Q2_3, income_cat, Q2_10, new_Q4, Q1_1), factor)) %>%
  dplyr::select(Q2_1, new_Q2_2,age_cat,new_Q2_3, income_cat, Q2_10, new_Q4, Q1_1)
 
demo_table <- sumtable(DEMO_dd)


```

## Visualize socio-demographic feature

```{r}

p0_job <-ggplot(DEMO_dd[!is.na(DEMO_dd$Q1_1),],mapping = aes(x=as_factor(Q1_1),fill = age_cat)) + 
  geom_bar(position = 'dodge',na.rm = T) +
  scale_fill_grey(name="Age category",
                  breaks=c("1", "2", "3","4","5"),
                  labels=c("18-19", "20-24", "25-29","30-34","35-40")) + 
  theme_classic(base_size = 18) + theme(legend.position = "top") + 
  labs(title = "Distribution plot of age per type of employment (a)",x = "Employment", y = "No. of participants") + 
  scale_x_discrete(labels = c('Has job','No job\n(full-time student)','No job\n(non full-time student)'))


p1_income <- ggplot(DEMO_dd[!is.na(DEMO_dd$income_cat),],
             mapping = aes(x=as_factor(income_cat),fill = age_cat)) + 
  geom_bar(position = 'dodge',na.rm = T) +
  geom_vline(aes(xintercept = 2), linetype="dashed", color="blue", size=1) +
  theme_classic(base_size = 18) + theme(legend.position = "none") + 
  scale_fill_grey()+
  labs(title = "Distribution plot of age per personal income category (b)",x = "Personal income",y = "No. of participants") + 
  scale_x_discrete(labels = c('Below HK$10,000',
                              'HK$10,000 - 19,999',
                              'HK$20,000 - 29,999',
                              'HK$30,000 - 39,999',
                              'HK$40,000 - 49,999',
                              'HK$50,000 - 59,999',
                              'HK$60,000 - 69,999',
                              'HK$70,000 - 79,999',
                              'HK$80,000 or above'))

# median(as.numeric(DEMO_dd$income_cat),na.rm = TRUE)
#> [1] 2


p2_edu <-ggplot(DEMO_dd[!is.na(DEMO_dd$Q2_10),],
             mapping = aes(x=as_factor(Q2_10),fill = age_cat)) + 
  geom_bar(position = 'dodge',na.rm = T) +
  geom_vline(aes(xintercept = 5), linetype="dashed", color="blue", size=1) +
  theme_classic(base_size = 18) + theme(legend.position = "none") + 
  scale_fill_grey() + 
  labs(title = "Distribution plot of age per level of educational attainment (c)",x = "Educational attainment", y = "No. of participants") + 
  scale_x_discrete(labels = c('Grade 6 or below',
                              'Grade 7-9',
                              'Grade 10-11',
                              'Grade 12-13',
                              'Higher Diploma or Associate Degree',
                              'Bachelor’s degree',
                              'Master’s degree or above'))
# median(as.numeric(DEMO_dd$Q2_10),na.rm = TRUE)
#> [1] 5


p3_house<-ggplot(DEMO_dd[!is.na(DEMO_dd$new_Q4),],
             mapping = aes(x=as_factor(new_Q4),fill = age_cat)) + 
  geom_bar(position = 'dodge',na.rm = T) +
  theme_classic(base_size = 18) + theme(legend.position = "none") + 
  scale_fill_grey() + 
  labs(title = "Distribution plot of age per type of homeownership (d)",x = 'Homeownership',y = "No. of participants") + 
  scale_x_discrete(labels = c('Owned Housing', 'Rented Housing'))

demo_plot <- plot_grid(p0_job, p1_income, p2_edu, p3_house, nrow = 4)
```

# Examination of four hypothesis

```{r}
hyp_dd <- imported %>% 
  mutate(new_Q2_2 = case_when(Q2_2 == 1 ~ 0, Q2_2 == 2 ~ 1),
         new_Q2_3 = case_when(Q2_3 == 1 | Q2_3 == 3 | Q2_3 == 4 ~ 1,
                              Q2_3 == 2 | Q2_3 == 5 | Q2_3 == 6 ~ 2),
         new_Q4 = case_when(Q4 <=5 ~ 0, Q4 >= 6 & Q4 <= 12 ~ 1)
  ) %>% 
  mutate(Q1_1 = case_when(Q1_1 ==1 ~ 1, 
                          Q1_1 ==2 | Q1_1==3 ~2)) %>% 
  mutate(across(c(new_Q2_2,new_Q2_3, Q1_1,new_Q4), factor))
 
```

## Construct three predictors and one outcome variable

```{r}
#> HC: 63, 56, 58, 59, 61, 60
#> SEC: 23, 21R, 62R, 26R, 6R, 31R, 25R, 27, 46, 22R, 35,  24, 36, 37R, 44, 29R
#> EI: 51, 52, 53, 54
#> CHC:  2, 47, 43, 55, 81, 79, 34, 42

#Housing challenge -  6 items
hc_scale <- c("D_Q63", "D_Q56", "D_Q58","D_Q59","D_Q61","D_Q60")
#Socio-economic challenges - 16 items
sec_scale <- c("B_Q23", "n_r_21", "n_r_62", "n_r_26", "n_r_6", "n_r_31", "n_r_25", "B_Q27", "C_Q46","n_r_22", "C_Q35", "B_Q24","C_Q36","n_r_37", "C_Q44", "n_r_29") 
#Hardships associated with Entrepreneurship and Innovation - 4 items
ei_scale <- c("D_Q51", "D_Q52", "D_Q53","D_Q54") 
#MC-HK convergence - 8 items
chc_scale <- c("B_Q2","C_Q47", "C_Q43","D_Q55", "G_Q81", "F_Q79", "C_Q34", "C_Q42") 


ei_scaled <- hyp_dd %>% dplyr::select(!!!ei_scale)
hc_scaled <- hyp_dd %>% dplyr::select(!!!hc_scale)
sec_scaled <- hyp_dd %>% dplyr::select(!!!sec_scale)
chc_scaled <- hyp_dd %>% dplyr::select(!!!chc_scale)

ltm::cronbach.alpha(hc_scaled, na.rm = TRUE)
ltm::cronbach.alpha(sec_scaled, na.rm = TRUE)
ltm::cronbach.alpha(ei_scaled, na.rm = TRUE)
ltm::cronbach.alpha(chc_scaled, na.rm = TRUE)

hyp_dd <- hyp_dd %>% 
  mutate(hc_avg = rowMeans(select_at(., hc_scale),na.rm = TRUE)) %>% 
  mutate(sec_avg = rowMeans(select_at(., sec_scale),na.rm = TRUE)) %>% 
  mutate(ei_avg = rowMeans(select_at(., ei_scale),na.rm = TRUE)) %>% 
  mutate(chc_avg = rowMeans(select_at(., chc_scale),na.rm = TRUE))

mean(hyp_dd$hc_avg)
mean(hyp_dd$sec_avg)
mean(hyp_dd$ei_avg)
mean(hyp_dd$chc_avg)

```

## Visualize distribution of predictors and outcome variables conditioned by age

```{r}

hc_age <- ggplot(hyp_dd, mapping = aes(x = as_factor(age_cat),y = hc_avg, fill = as_factor(age_cat))) + 
  scale_fill_grey() + 
  # add half-violin from {ggdist} package
  stat_halfeye(adjust = .5,# custom bandwidth
               justification = 0,# move geom to the right
               .width = 0.5,# remove slab interval
               point_colour = NA) +
  geom_boxplot(color = "blue",width = .5, outlier.colour="blue",outlier.shape=7,outlier.size=4,notch=TRUE,notchwidth=0.5) + 
  labs(title="Distribution plot of housing challenges (HC) per age category (a)", y = "HC",x = "",fill="Age category") + 
  geom_hline(aes(yintercept = 4.05),linetype="dashed", color="blue", size=1) +
  theme_classic(base_size = 18) + 
  theme(legend.position = "top", axis.ticks = element_blank(), axis.text.x = element_blank()) 
#mean(hyp_dd$HC) #> 4.05

ss_age <- ggplot(hyp_dd, mapping = aes(x = as_factor(age_cat),y = sec_avg, fill = as_factor(age_cat))) + 
  scale_fill_grey() + 
  stat_halfeye(adjust = .5,justification = 0,.width = 0.5,point_colour = NA) +
  geom_boxplot(color = "blue",width = .5, outlier.colour="blue",outlier.shape=7,outlier.size=4,notch=TRUE,notchwidth=0.5) + 
  labs(title="Distribution plot of socio-economic challenges (SEC) per age category (b)",y = "SEC",x = "") + 
  geom_hline(aes(yintercept = 3.46),linetype="dashed", color="blue", size=1) +
  theme_classic(base_size = 18) + 
  theme(legend.position = "none",axis.ticks = element_blank(), axis.text.x = element_blank()) 
#mean(hyp_dd$ss) #> 3.46

ei_age <- ggplot(hyp_dd, mapping = aes(x = as_factor(age_cat),y = ei_avg, fill = as_factor(age_cat))) + 
  scale_fill_grey() + 
  stat_halfeye(adjust = .5,justification = 0,.width = 0.5,point_colour = NA) +
  geom_boxplot(color = "blue",width = .5, outlier.colour="blue",outlier.shape=7,outlier.size=4,notch=TRUE,notchwidth=0.5) + 
  labs(title="Distribution plot of hardships associated with entrepreneurship and innovation (EI) per age category (c)",y = "EI",x = "") + 
  geom_hline(aes(yintercept = 4),linetype="dashed", color="blue", size=1) +
  theme_classic(base_size = 18)  + 
  theme(legend.position = "none",axis.ticks = element_blank(), axis.text.x = element_blank())
#mean(hyp_dd$EI) #> 4

hci_age <- ggplot(hyp_dd, mapping = aes(x = as_factor(age_cat),y = chc_avg, fill = as_factor(age_cat))) + 
  scale_fill_grey() + 
  stat_halfeye(adjust = .5,justification = 0,.width = 0.5,point_colour = NA) +
  geom_boxplot(color = "blue",width = .5, outlier.colour="blue",outlier.shape=7,outlier.size=4, notch=TRUE,notchwidth=0.5) + 
  labs(title="Distribution plot of Mainland China–Hong Kong convergence (CHC) per age category (d)",x="Age category", y = "CHC") + 
  geom_hline(aes(yintercept = 2.87),linetype="dashed", color="blue", size=1) +
  theme_classic(base_size = 18) + 
  theme(legend.position = "none")
#mean(hyp_dd$HCI) #> 2.87 

ind_plot <- plot_grid(hc_age, ss_age,ei_age,hci_age,nrow = 4)
  

```

## Test HYP1

Hypothesis 1 (H1): The perception of the housing challenges is negatively related to MC-HK convergence. That is, the more the young people perceived challenges in their housing conditions, the lower their acceptance of MC-HK convergence.

```{r}
# HC-CHC: supported
hyp1 <- lm(chc_avg ~ Q2_1+new_Q2_2+new_Q2_3+Q2_7_inco+Q1_1+new_Q4 + hc_avg, hyp_dd)
```

## Test HYP2

Hypothesis 2 (H2): Higher education predicts lower acceptance of MC-HK convergence. That is, the higher the young people's level of education, the lower their acceptance of MC-HK convergence.

```{r}
#education - CHC: supported
hyp2 <- lm(chc_avg ~ Q2_1+new_Q2_2+new_Q2_3+Q2_7_inco+Q1_1+new_Q4 + Q2_10, hyp_dd)
```

## Test HYP3

Hypothesis 3 (H3): The perception of the socio-economic challenges is negatively related to MC-HK convergence. That is, the more the young people perceived challenges in their socio-economic conditions, the lower their acceptance of MC-HK convergence.

```{r}
#SEC - CHC: supported
hyp3 <- lm(chc_avg ~ Q2_1+new_Q2_2+new_Q2_3+Q2_7_inco+Q1_1+new_Q4 + sec_avg, hyp_dd)
```

## Test HYP4

Hypothesis 4 (H4): The perception of the hardships associated with entrepreneurship and innovation is positively related to MC-HK convergence. That is, the more the young people perceived hardships associated with entrepreneurship and innovation, the higher their acceptance of MC-HK convergence.

```{r}
#EI - CHC: not supported
hyp4 <- lm(chc_avg ~ Q2_1+new_Q2_2+new_Q2_3+Q2_7_inco+Q1_1+new_Q4 + ei_avg, hyp_dd)
```

## Visualization of effect of four hypothesis

```{r}
coef_names <- c("Age" = "Q2_1",
                "Gender" = "new_Q2_21",
                "Marital status (married = 0)" = "new_Q2_32",
                "Personal income" = "Q2_7_inco",
                "Employment (has job = 0)" = "Q1_12",
                "Homeownership (owned = 0)" = "new_Q41",
                "Housing challenges (HC)" = "hc_avg",
                "Educational attainment" = "Q2_10",
                "Socio-economic challenges (SEC)" = "sec_avg",
                "Hardships associated with\nentrepreneurship and innovation (EI)" = "ei_avg"
                )
reg_plot <- jtools::plot_summs(hyp1,hyp2,hyp3,hyp4,
                               coefs = coef_names,
                               inner_ci_level = .9,
                               model.names = c("Model H1","Model H2","Model H3", "Model H4"),
                               colors = "Greys", point.size = 10) + 
  theme_classic(base_size = 24) +theme(legend.position = "top")
export_summs(hyp1,hyp2,hyp3,hyp4, #scale = TRUE, robust = TRUE,
             error_format = "[{conf.low}, {conf.high}]",
             model.names = c("Model of H1","Model of H2","Model of H3","Model of H4"),
             coefs = coef_names)
             #to.file = "docx", file.name = "output.docx")

```
